---
title: "Regression Project"
author: "Kevin Chavez Lopez, Rian Russell, and Yating Wu"
date: "February 10, 2026"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Offer a preliminary description of the data set. For example, indicate the size of the data source, describe the variables, and include any other data profile information that would be of interest.

The dataset that we will be working with contains 1873 observations of nine rats performing a perceptual decision-making task. This dataset contains a total of 14 columns that describe the following: Four categorical variables:

- Name
- Session
- Sex
- Cue

Ten quantitative variables:

- Time (potentially useless as it only represents the time at which the event on the corresponding row occured!)
- Sampling (Time that the rat spent at the center port)
- Latency (Time between departing the center port and nose-poking a side port)
- Cue (Three brightness levels: 1, 4, 16 pixels)
- Presented (What side the given Cue was presented on. 0 = Left, 1 = Right)
- Choice (What side the rat nosepoked. 0 = Left, 1 = Right)
- Response (The outcome of such choice. 0 = Error, 1 = Correct)
- ITI (Time difference BETWEEN trials)
- Velocity (The max velocity that the rat achieved during a trial)
- Time2peak (How long it took to reach the max velocity above)
- RT (Sampling + Latency variables. Combined to determine)

3. Using R code, produce a full Regression Model that consists of quantitative and categorical variables. Make use of the R generated dummy variable matrices.

```{r}

library(tidyverse)

```

```{r}

cleanData <- read_csv("STAT615_Project1_CLEAN.csv")
dim(cleanData)

```

We want to look at the difference between cue (independent) on response time (dependent).

```{r}

lm(cue ~ rt, data = cleanData)

```

